Prediction of Drinking Water Treatment Process Chemical Doses

### 2025-12-16 Paper Draft.Rmd
Looked very weird on the github hopefully i fixed it

### Linear Regression

To model FeCl dosing using linear regression, we fit six different linear regression models that varied in their choice of predictors and inclusion of differing interaction terms. The models incorporated current and lagged values of temperature, pH, conductivity, and turbidity, allowing us to account for delayed effects in the system from previous days. Several interactions were tested, including temperature-pH and temperature-conductivity, to capture potential nonlinear relationships between water quality variables. Turbidity was ultimately dropped from the final models, as it consistently preformed poorly as a predictor for FeCl dosing.
```{r}

>>>>

### Linear Regression
To model FeCl dosing using linear regression, we fit six different linear regression models that varied in their choice of predictors and inclusion of differing interaction terms. The models incorporated current and lagged values of temperature, pH, conductivity, and turbidity, allowing us to account for delayed effects in the system from previous days. Several interactions were tested, including temperature-pH and temperature-conductivity, to capture potential nonlinear relationships between water quality variables. Turbidity was ultimately dropped from the final models, as it consistently preformed poorly as a predictor for FeCl dosing.
